Extended Data

### 2022-03-23 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd
#129

<!--QUILT PLOT METHODS-->
For the analysis of correlation between RWI and climate variables, we obtained monthly *T~max~* and *T~min~* data for 1901-2019 from CRU v.4.04 [@harris_version_2020].
<!-- this sentence needs some work-->Correlations between monthly climate and RWI were assessed in R **v 4.0**[@rcoreteam_language_2020]<!--check reference year--> using the packages *dplR*[@bunn_dendrochronology_2008] <!-- did we actually use this package?--> and *bootRes*[@zang_dendroclimatic_2013] to assess correlations, provide bootstrapped confidence intervals for these relationships, and create summary figures (Fig. `r tree_rings`, Extended Data Figures 6-7) following the methods of Ref.[@biondi_dendroclim2002_2004]. 
Our analysis focused on assessing correlations of RWI to months spanning from January through September of the current year (presented in Fig. `r tree_rings`, `r EDF_tree_rings_TMIN`).
To test for potential lag effects of spring temperatures on growth the following year, we also ran a version of the analysis extending back to include climate of every month of the previous year (`r EDF_tree_rings_TMAX_extended`).
Correlations and significance levels for months March-August are given in `r chron_table`.

>>>>

<!--QUILT PLOT METHODS-->
For the analysis of correlation between RWI and climate variables, we obtained monthly *T~max~* and *T~min~* data for 1901-2019 from CRU v.4.04 [@harris_version_2020].
<!-- this sentence needs some work. CD: maybe Valentine can help with this-->Correlations between monthly climate and RWI were assessed in R **v 4.0**[@rcoreteam_language_2020]<!--check reference year. CD: this is the reference year that the function "citation()" give me, so it should be correct.--> using the packages *dplR*[@bunn_dendrochronology_2008] <!-- did we actually use this package? CD: Yes, at the very least we used modified functions from this package.--> and *bootRes*[@zang_dendroclimatic_2013] to assess correlations, provide bootstrapped confidence intervals for these relationships, and create summary figures (Fig. `r tree_rings`, Extended Data Figures 6-7) following the methods of Ref.[@biondi_dendroclim2002_2004]. 
Our analysis focused on assessing correlations of RWI to months spanning from January through September of the current year (presented in Fig. `r tree_rings`, `r EDF_tree_rings_TMIN`).
To test for potential lag effects of spring temperatures on growth the following year, we also ran a version of the analysis extending back to include climate of every month of the previous year (`r EDF_tree_rings_TMAX_extended`).
Correlations and significance levels for months March-August are given in `r chron_table`.
